Verifying Demonstrations

### 2018-11-01 paper/intro.tex
rephrased related work phrasing in intro

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party), or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with 
their identity and that any witnessing is also unlinkable.

\emph{Contributions.} In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
\sonja{commented out for repetition:This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.}

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} 
for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against Brands-Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
\emph{Outline.} 
The paper is organized as follows.
First, in \cref{system-model}, we define and formalize the notion of protest 
and define the desired verifiability properties.
We also present our system and adversary model together with desired privacy 
properties.
Next, in \cref{related-work}, we discuss related work in terms of these 
properties.
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
In \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr 
protocol, different from that originally proposed by 
\textcite{DistanceBounding}.
We provide a proof of its security (all desired \ac{DB} properties) 
\daniel{Check that this is true before publication.} and formally verify it 
using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
In \cref{Protocol}, we present \PRIVO, the protocol constructed from these 
building blocks.
This is followed by an analysis of its security and privacy 
(\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in 
\cref{Conclusion}.
\sonja{add (sub) sections for performance and verification}

>>>>

Finally, one important observation about crowd-counting that has not been adequately addressed in the design of current crowd-counting solutions is that it actually is an adversarial setting. 
Indeed, going back to our example, Alice the activist has an incentive to increase the tallied number of participants, whereas Grace (and possibly other entities) have an incentive to decrease it.
In this case, we are left with two options: either we trust Alice or Grace (or another third party), or we have to be able to verify their claims ourselves.
In this paper, our main objective is to provide a scheme preventing both Alice and Grace from cheating (\ie their claim should be verifiable).
To solve this issue, we need a verifiable participation count that can resist Sybil attacks while still preserving the participants' privacy to the extent possible given their physical presence at the protest. 
More precisely, our solution will not be able to magically prevent an observer (physically present or looking at photos or videos) from recognizing a particular individual at a protest. 
Nonetheless, we can ensure that none of the digital traces generated by a participant due to our scheme can be associated with their identity and that any witnessing is also unlinkable.

\emph{Contributions.} In this paper, our first main contribution is to propose \PRIVO, a privacy-preserving scheme providing a way to securely estimate crowd count in protests.
%\sonja{commented out for repetition:This verification system does not incur any additional risk to protesters' privacy beyond the ones related to physically participating in the protest in the first place.}
%Seb: I am ok with the change done

Our second contribution is an adaptation of the Schnorr protocol~\cite{Schnorr} for \ac{DB}, but which is different from that of \textcite{DistanceBounding}.
Our adaptation fulfills all the requirements for modern \ac{DB} protocols, including \ac{DBDH} (which was an attack against the original protocol of Brands and Chaum).
More importantly, it is public-key, handles malicious impersonating verifiers, fulfills \ac{DBTF} and other types of resistance (see \cref{distance-bounding}), and provides a \ac{PK} for discrete logarithms.
The latter allows us to replace the use of the plain Schnorr protocol in the \ac{ZKPK} used in anonymous credentials,
%\seb{once again I think it is too strong to say that are the first to provide distance-bounding anonymous credentials as a a distance-bounding anonymous protocol can already be considered an anonymous credential in the sense that it allows to authenticate anonymously in addition of providing proximity testing
%and thus we are, to the best of our knowledge, the first to provide \ac{DB} anonymous credentials.}
%\sonja{Daniel, can you contrast that with the other DB AC approaches, what are they not general enough for, or what can we do they can't?}
and thus we are, to the best of our knowledge, the first to provide \emph{general} (\ie attribute-based, not only identity-based) \ac{DB} anonymous credentials.
\emph{Outline.} 
The paper is organized as follows.
First, in \cref{system-model}, we formalize the notion of protest and define the desired verifiability properties.
We also present our system as well as the adversary model together with desired privacy properties.
Next, in \cref{related-work}, we discuss related work in terms of these properties, first the crowd counting methods that are classically used and then work on location proof systems that inspired \PRIVO. 
In \cref{building-blocks}, we give the relevant background on the building blocks of our solution.
Afterwards in \cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, different from that originally proposed by \textcite{DistanceBounding}.
We provide a proof of its security (\ie that fact that it achieved all desired \ac{DB} properties) 
%\daniel{Check that this is true before publication.} 
and formally verify it using Tamarin~\cite{TamarinDB}.
This version of the Schnorr protocol can then be used to do general \ac{DB} 
anonymous credentials.
Then \cref{Protocol}, we present \PRIVO, the protocol constructed from these building blocks, before analyzing its security and privacy (\cref{SecurityAnalysis}).
Finally, we conclude with a discussion in \cref{Discussion} and future work in \cref{Conclusion}.
%\sonja{add (sub) sections for performance and verification}

### 2018-11-01 paper/protest-model.tex

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every weekend for a few weeks duration.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the cause, \label{CauseIsTheCommonDenominator} while the location (or area) considered 
varies over time.

@@

\begin{definition}[Subprotest, Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in \ZZ_{2^\lambda}\) is the identifier of the cause of the protest,
  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location (the topological connectedness is not necessary).
  A \emph{protest} is a set of subprotests sharing the same \(\cid\).
\end{definition}

>>>>

%\emph{Defining the concept of protest.} 
To be able to estimate the participation count for a protest, we first need to define this concept and which quantity should be counted.
Let us start by considering some examples.
During the demonstrations against the South Korean president in Seoul in 2016
\blockcquote{2016DemonstrationsInSeoul}{%
  \textins*{t}he rallies stretch\textins{ed} from midday to late night --- some people stay\textins{ed} for several hours, others just several minutes%
}.
These rallies were all in the same location in the capital and repeated every weekend for a few weeks duration.
The Women's Marches in 2017~\cite{2017WomensMarchesInUS}, on the other hand, occurred in parallel in many locations.
We also have the Venezuelan demonstrations in 2017 in which \blockcquote{2017VenezuelaProtestFrequency}{%
  anti-government demonstrators have staged daily protests across Venezuela%
} while
\blockcquote{AlJazeeraOnVenezuela2017}{%
  pro-government workers sang and danced as they staged a rival march to show their support for the president's controversial plan to rewrite the constitution%
}.
Generalizing from these examples, the minimal common part is the 
cause,\label{CauseIsTheCommonDenominator} while the location (or area) 
considered varies over time.

@@

\begin{definition}[Subprotest, Protest]\label{DefProtest}
  A \emph{subprotest} is a tuple \((\cid, t, l)\) in which \(\cid\in 
    \ZZ_{2^\lambda}\), for some fixed \(\lambda\in \NN\), is the identifier of 
  the cause of the protest,
  \(t \subseteq \RR\) is a time period and \(l \subseteq \RR^2\) is the location (the topological connectedness is not necessary).
  A \emph{protest} is the set of subprotests sharing the same \(\cid\).
\end{definition}

### 2018-11-01 paper/protocol.tex

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \PRIVOjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
Afterwards, this identifier is used to create the protest-specific identifier for the protester, \(\pid\gets \ACprf[_{\sk}][\cid]\) (in 
\cref{fig:ProofFig,fig:ProtocolOverview}).
More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, k, r)\)).
The protester should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).

\begin{figure}
  \centering
  \small
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
    witness's key \(\sk_W\) and the protester's \(\pid\).
    \(t_s, t_s'\) are the last heads of the blockchain seen by the protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
    The protester constructs \(\prf_P\) analogously.
  }%
  \label{fig:ProofFig}
\end{figure}%

@@

\emph{Joining as a witness: \(t_s'\gets \PRIVOjoin_W\).}
The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will be set the start of the time interval of creation for the proof share.

\emph{Participation: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The protester sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the protester and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the protester as the prover 
and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k_P+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows.
(Remember that this \ac{PK} should be run as \iac{PPK} and repeated multiple 
times to achieve security.)
The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the protester computes
\begin{align*}
  s_k &= -ck + r_k, \\
  s_r &= -cr + r_r, \\
  s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
  = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the protester.
As a consequence, both the protester and the witness have the tuple \(\psh = 
  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
protester (\cref{fig:ProofFig}).

@@

To verify the participation count for a protest \(P = (\cid, t, l)\) (see 
\cref{DefProtest}), a verifier must download all the proof shares \(\psh_i =   
  (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, t_e^{\prime   
    (i)}, l_i, \prf_{\pid_j}^{(i)}, \prf_{\wid_i})\) for each protester \(j\) 
from the blockchain, verify \(\prf_{\pid_j}^{(i)}\), \(\prf_{\wid_i}\) and that 
the interval \(\interval{\max(t_s^{(i)}, t_s^{\prime (i)})}{\min(t_e^{(i)}, 
    t_e^{\prime (i)})}\) is a subset of \(t\) and that \(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.

In the case \emph{without} trusted witnesses, the verifier simply define 
\(\str[\prf_{\pid_i, P}] = |\prf_{\pid_i, P}|\) and set \(\theta\) to the 
desired threshold.

In the case \emph{with} trusted witnesses, each trusted witness must inform the 
verifier of which proof shares that he or she has signed, \eg by giving a list 
of all such proof shares or digitally sign each proof share.
Then the verifier can define \[
  \str[\prf_{\pid_i, P}] = \begin{cases}
    1 & \text{if \(\prf_{\pid_i, P}\) is such a proof share} \\
    0 & \text{otherwise}
  \end{cases}
\] and sets \(\theta = 1\).

>>>>

\emph{Joining as a protester: \((\pid, t_s)\gets 
    \PRIVOjoin[_P][\text{manifesto}]\).}
A protester who wants to join the protest will use the manifesto to compute an identifier for the cause by hashing the manifesto, \(\cid\gets \Hash[\mfst]\).
Afterwards, this identifier is used to create the protest-specific identifier 
for the protester, \(\pid\gets \ACprf[_{\sk_P}][\cid]\) (in 
\cref{fig:ProofFig,fig:ProtocolOverview}).
More specifically, \(\pid = g_T^{1/(k+\cid)}\) (remember that \(\sk = (\sigma, k, r)\)).
The protester should also receive a time-correlated random value from the time-stamping service, \(t_s\gets \TSget\).

\begin{figure}
  \centering
  \small
  \includegraphics{proofshare.tikz}
  \caption{%
    Structure of a proof share.
    The protest (cause) identifier \(\cid\) is the hash value of the manifesto.
    The protester \(P\)'s identifier \(\pid\) is computed using the protester's key \(\sk_P\) and \(\cid\).
    The witness \(W\)'s protester-specific identifier \(\wid\) is computed using the
    witness's key \(\sk_W\) and the protester's \(\pid\).
    \(t_s, t_s'\) are the hashes of the head blocks in the ledger seen by the 
    protester and witness, respectively, and \(l\) is an area.
    All values are signed by the witness (signature \(\prf_W = \SPK[\sk_W][\wid 
      = \dotsb][\cid, \pid, \wid, t_s, t_s', l]\)) while also proving the 
    correctness of \(\wid\) and knowledge of a signature on \(\sk_W\).
    The protester constructs \(\prf_P\) analogously.
  }%
  \label{fig:ProofFig}
\end{figure}%

@@

\emph{Joining as a witness: \(t_s'\gets \PRIVOjoin_W\).}
The witness should simply get a time-correlated random value from the time-stamping service, \(t_s'\gets \TSget\).
Note that we do this for redundancy, the newest of \(t_s\) and \(t_s'\) will 
set the start of the time interval of creation for the proof share.

\emph{Participation: \(\pi\gets
    \Proto{\PRIVOparticipate[\cid, \sk_P]}{\PRIVOwitness[\sk_W, \spk]}\),}
In the participation phase, the protester and the witness construct the proof share of the protester (\cref{fig:ProofFig}).
The protester blinds his signature \(\sigma\) on his secret key by choosing \(r_1, r_2\rgets \ZZ_q^*\) and generates \(
  \tilde\sigma = (\tilde A = A^{r_1},
                  \tilde B = B^{r_1},
                  \tilde Z_B = Z_B^{r_1},
                  \hat C = C^{r_1 r_2}).
\) 
Note that it is not necessary to compute a new \(\tilde\sigma\) more than once per \(\pid\).
The protester sends \((\pid, \tilde\sigma)\) to the witness.
The witness verifies that
\begin{align*}
  \tilde A          &\neq 1 \\
  e(g, \tilde B)    &= e(Y, \tilde A) \\
  e(g, \tilde Z_B)  &= e(Z, \tilde B).
\end{align*}
Both the protester and the witness compute
\begin{align*}
  v &= e(g, \hat C) \\
  v_x &= e(X, \tilde A) \\
  v_{xy} &= e(X, \tilde B) \\
  v_{xy}' &= e(X, \tilde Z_B).
\end{align*}
Afterwards, they run the following \ac{PPK} with the protester as the prover 
and the witness as the verifier:
\begin{multline*}
  \mleftright
  \PPK\left\{(k, r, r') : v^{r'} = v_x v_{xy}^k v_{xy}^{\prime r} \land
    \pid = g_T^{1/(k_P+\cid)} \right\}.
\end{multline*}
in which \(r' = 1/r_2\).
We can rewrite \(\pid = g_T^{1/(k+\cid)}\) as \(\pid^k = g_T g_T^{-\cid}\).
Afterwards, the \ac{PK} can be designed as follows.
(Remember that this \ac{PK} should be run as the \ac{PPK} in 
\cref{DB-anon-cred} and repeated multiple times to achieve security.)
The protester chooses \(r_k, r_r, r_{r'}\rgets \ZZ_q\) uniformly at random, 
sets \(R_1 = v^{r_{r'}} v_{xy}^{r_k} v_{xy}^{\prime r_r}\) and \(R_2 = 
  \pid^{r_k}\) and sends \(R_1, R_2\) to the witness.
The witness replies with a challenge \(c\).
Afterwards, the protester computes
\begin{align*}
  s_k &= -ck + r_k, \\
  s_r &= -cr + r_r, \\
  s_{r'} &= cr' + r_{r'}
\end{align*}
and forwards them to the witness.
The witness checks whether
\begin{align*}
  v_x^c R_1 &\overset{\mathclap{?}}{=} v^{s_{r'}} v_{xy}^{s_k} v_{xy}^{\prime 
    s_r}, \\
  \mleft(g_T \pid^{-\cid}\mright)^{-c} R_2 &\overset{\mathclap{?}}{=} 
  \pid^{s_k}.
\end{align*}
If the proof succeeds, the witness computes \(\wid\gets \ACprf[_{\sk_W}][\pid] 
  = g_T^{1/(k_W+\pid)}\) (as above).
Following this, the witness returns \((\wid, t_s', l)\) to the protester.
As a consequence, both the protester and the witness have the tuple \(\psh = 
  (\cid, \pid, \wid, t_s, t_s', l)\), which forms a proof share for the 
protester (\cref{fig:ProofFig}).

@@

To verify the participation count for a subprotest \(\sprtst = (\cid, t, l)\) 
(see \cref{DefProtest}), a verifier must download all the proof shares \[
  \psh_i =   (\cid, \pid_j, \wid_i, t_s^{(i)}, t_s^{\prime (i)}, t_e^{(i)}, 
  t_e^{\prime   (i)}, l_i, \prf_{\pid_j}^{(i)}, \prf_{\wid_i})
\] for each protester \(j\) from the ledger, verify \(\prf_{\pid_j}^{(i)}\), 
\(\prf_{\wid_i}\) and that the interval \(\interval{\max(t_s^{(i)}, t_s^{\prime 
      (i)})}{\min(t_e^{(i)}, t_e^{\prime (i)})}\subseteq t\) and that 
\(l_i\subseteq  l\).
Any proof share that does not verify correctly will be discarded.
At this point, the verifier has constructed the set \(S\) from 
\cref{DefProofShares} and can thus construct any participation proof 
\(\prf_{\pid_j, P}\) as in \cref{DefParticipationProof}.
Now the verifier can compute the participation count \(|\prfs_P^{\str, 
    \theta}|\) as in \cref{DefParticipationCount}.

In the case \emph{without} trusted witnesses, the verifier simply define 
\(\str[\prf_{\pid_j, P}] = |\prf_{\pid_j, P}|\) and set \(\theta\) to the 
desired threshold.

In the case \emph{with} trusted witnesses, each trusted witness must inform the 
verifier of which proof shares that he or she has signed, \eg by giving a list 
of all such proof shares or digitally sign each proof share\footnote{%
  To achieve witness privacy in this situation, one could employ a group or 
  ring signature scheme for all trusted witnesses.
  Then one learns that at least one trusted witness must have been there.
}.
Then the verifier can define \[
  \str[\prf_{\pid_j, P}] = \begin{cases}
    1 & \text{if \(\exists \psh_i\in \prf_{\pid_j, P}\) that is such a proof 
      share} \\
    0 & \text{otherwise}
  \end{cases}
\] and sets \(\theta = 1\).
